Constraining gravitational wave amplitude birefringence with GWTC-3

### 2023-04-03 src/tex/ms.tex
minor wording

Here we present the measurement on all parameters we consider relevant for GW170818, of which Fig.~\ref{fig:corner_GW170818} in the main text represents a subset.
The regular \ac{GR} analysis (GR; orange) and the birefringent analysis (BR; blue) both show notable features.

The GR analysis stands out for its relatively confident identification of the spin angles, $\theta_{1/2}$ and $\phi_{JL}$, as well as the phase and polarization angles, $\phi_{\rm ref}$ and $\psi$.
Of the former, the two $\theta_{1/2}$ parameters encode the tilts of the component \acp{BH} with respect to the orbital angular momentum, $\vec{L}$, while $\phi_{JL}$ is the angle between the projections of $\vec{L}$ and the total angular momentum, $\vec{J}$, along the orbital plane;
of the latter, $\phi_{\rm ref}$ is an overall reference phase, and $\psi$ encodes the orientation of the binary within the plane of the sky \cite{Isi:2022mbx}.
All these parameters are anchored to a reference point in the evolution of the inspiral, which in this case corresponds to the time at which the dominant mode of the observed \ac{GW} signal reaches 20 Hz at the detector (spin angles may be better identified by using a more physical reference point \cite{Varma:2021csh}).
It is unusual for these angles to be well constrained, which suggests that this event displays a particular phase and polarization signature.

>>>>

Here we present the measurement on all parameters we consider relevant for GW170818, of which Fig.~\ref{fig:corner_GW170818} in the main text represents a subset.
Figure \ref{fig:corner_GW170818_appendix} shows the the regular \ac{GR} analysis (GR; orange) and the birefringent analysis (BR; blue), both of which show notable features.

The GR analysis stands out for its relatively confident identification of the spin angles, $\theta_{1/2}$ and $\phi_{JL}$, as well as the phase and polarization angles, $\phi_{\rm ref}$ and $\psi$.
Of the former, the two $\theta_{1/2}$ angles encode the tilts of the component \acp{BH} with respect to the orbital angular momentum, $\vec{L}$, while $\phi_{JL}$ is the angle between the projections of $\vec{L}$ and the total angular momentum, $\vec{J}$, along the orbital plane;
of the latter, $\phi_{\rm ref}$ is an overall reference phase, and $\psi$ encodes the orientation of the binary within the plane of the sky \cite{Isi:2022mbx}.
All these parameters are anchored to a reference point in the evolution of the inspiral, which in this case corresponds to the time at which the dominant mode of the observed \ac{GW} signal reaches 20 Hz at the detector (spin angles may be better identified by using a more physical reference point \cite{Varma:2021csh}).
It is unusual for these angles to be well constrained, which suggests that data for this event display a particular phase and polarization signature.
